\begin{thebibliography}{10}

\bibitem{Cheung:1995ei}
  N.~E. Cheung et~al.
  \newblock {Calibration of the polarimeter POMME at proton energies between
    1.05-GeV and 2.4-GeV}.
  \newblock {\em Nucl. Instrum. Meth.}, A363:561--567, 1995.

\bibitem{Azhgirey:2004yk}
  L.S. Azhgirey, V.A. Arefev, S.N. Basilev, Yu.P. Bushuev, V.V. Glagolev, et~al.
  \newblock {Measurement of analyzing powers for the reaction $\vec p + CH_2$ at
    $p_p$ = 1.75-GeV/c - 5.3-GeV/c}.
  \newblock {\em Nucl. Instrum. Meth.}, A538:431--441, 2005.

\bibitem{Lehar:2001wq}
  F.~Lehar.
  \newblock {Current experiments using polarized beams of the JINR LHE
    accelerator complex}.
  \newblock {\em Phys. Part. Nucl.}, 36:501--528, 2005.
  \newblock [Fiz. Elem. Chast. Atom. Yadra36,955(2005)].

\bibitem{ALPOM2}
  V.P. Balandin et~al.
  \newblock {Measurement of analyzing power for the reaction $\vec p$ + CH$_2$ at
    polarized proton momentum of 7.5 GeV/c (ALPOM2 proposal)}.
  \newblock {\em Physics of Particles and Nuclei}, 45(1):330--332, 2014.

\bibitem{Kekelidze:2017ghu}
  V.~D. Kekelidze, V.~A. Matveev, I.~N. Meshkov, A.~S. Sorin, and G.~V.
  Trubnikov.
  \newblock {Project Nuclotron-based Ion Collider Facility at JINR}.
  \newblock {\em Phys. Part. Nucl.}, 48(5):727--741, 2017.

\bibitem{Kekelidze:2017ual}
  V.~D. Kekelidze.
  \newblock {NICA project at JINR: status and prospects}.
  \newblock {\em JINST}, 12(06):C06012, 2017.

\bibitem{Pacetti:2015iqa}
  Simone Pacetti, Rinaldo Baldini~Ferroli, and Egle Tomasi-Gustafsson.
  \newblock {Proton electromagnetic form factors: Basic notions, present
    achievements and future perspectives}.
  \newblock {\em Phys. Rep.}, 550-551:1--103, 2015.

\bibitem{Punjabi:2015bba}
  V.~Punjabi, C.~F. Perdrisat, M.~K. Jones, E.~J. Brash, and C.~E. Carlson.
  \newblock {The Structure of the Nucleon: Elastic Electromagnetic Form Factors}.
  \newblock {\em Eur. Phys. J.}, A51:79, 2015.

\bibitem{Akhiezer:1968ek}
  A.I. Akhiezer and M.~P. Rekalo.
  \newblock {Polarization phenomena in electron scattering by protons in the high
    energy region}.
  \newblock {\em Sov.Phys.Dokl.}, 13:572, 1968.

\bibitem{Akhiezer:1974em}
  A.I. Akhiezer and M.~P. Rekalo.
  \newblock {Polarization effects in the scattering of leptons by hadrons}.
  \newblock {\em Sov. J. Part. Nucl.}, 4:277, 1974.

\bibitem{Jones:1999rz}
  M.~K. Jones et~al.
  \newblock { $G_{Ep} / G_{Mp}$ ratio by polarization transfer in $\vec e p \to e
    \vec p$}.
  \newblock {\em Phys. Rev. Lett.}, 84:1398--1402, 2000.

\bibitem{Punjabi:2005wq}
  V.~Punjabi, C.F. Perdrisat, K.A. Aniol, F.T. Baker, J.~Berthot, et~al.
  \newblock {Proton elastic form-factor ratios to $Q^2$ = 3.5 GeV$^2$ by
    polarization transfer}.
  \newblock {\em Phys. Rev. C}, C71:055202, 2005.

\bibitem{Gayou:2001qd}
  O.~Gayou et~al.
  \newblock {Measurement of $G_{Ep} / G_{Mp}$ in $\vec e p \to e \vec p$ to $Q^2$
    = 5.6 GeV$^2$}.
  \newblock {\em Phys. Rev. Lett.}, 88, 2002.

\bibitem{Puckett:2011xg}
  A.J.R. Puckett, E.J. Brash, O.~Gayou, M.K. Jones, L.~Pentchev, et~al.
  \newblock Final analysis of proton form factor ratio data at $q^2 = 4.0$, 4.8
  and 5.6 gev$^2$.
  \newblock {\em Phys. Rev. C}, 85:045203, 2012.

\bibitem{Puckett:2010ac}
  A.J.R. Puckett, E.J. Brash, M.K. Jones, W.~Luo, M.~Meziane, et~al.
  \newblock {Recoil Polarization Measurements of the Proton Electromagnetic Form
    Factor Ratio to $Q^2$ = 8.5 GeV$^2$}.
  \newblock {\em Phys. Rev. Lett.}, 104:242301, 2010.

\bibitem{Puckett:2017flj}
  A.~J.~R. Puckett et~al.
  \newblock {Polarization Transfer Observables in Elastic Electron Proton
    Scattering at $Q^2 = $2.5, 5.2, 6.8, and 8.5 GeV$^2$}.
  \newblock {\em Phys. Rev.}, C96(5):055203, 2017.

\bibitem{Meziane:2010xc}
  M.~Meziane et~al.
  \newblock {Search for effects beyond the Born approximation in polarization
    transfer observables in $\vec e p$ elastic scattering}.
  \newblock {\em Phys. Rev. Lett.}, 106:132501, 2011.

\bibitem{PR12-07-109}
  C.F. Perdrisat, L.P. Pentchev, et~al.
  \newblock {Large Acceptance Proton Form Factor. Ratio Measurements at 13 and 15
    (GeV/c)$^2$. Using Recoil Polarization Method, Jefferson Lab Experiment
    E12-07-109}, 2007.

\bibitem{PR12-11-009}
  B.D. Anderson et~al.
  \newblock {The Neutron Electric Form Factor at $Q^{2}$ up to 7(GeV/c)$^{2}$
    from the reaction $^{2}\!H(\vec{e},e'\vec {n})$ via Recoil Polarimetry,
    Jefferson Lab Experiment E12-11-009}, 2011.

\bibitem{PR12-17-004}
  J.R.M. Annand et~al.
  \newblock {Measurement of the Ratio $\mathrm{G_{E}^{n}/G_{M}^{n}}$ by the
    Double-polarized $^{2}\!H(\vec{e},e'\vec{n})$ Reaction,Jefferson Lab
    Experiment E12-17-004}, 2017.

\bibitem{PR12-09-016}
  G.~Cates et~al.
  \newblock {Measurement of the Neutron Electromagnetic Form Factor Ratio
    $G_E^n/G^n_M$ at High $Q^2$,Jefferson Lab Experiment PR12-09-016}, 2009.

\bibitem{Becker:1999tw}
  J.~Becker et~al.
  \newblock {Determination of the neutron electric form-factor from the reaction
    $^3\!He(e,e' n)$ at medium momentum transfer}.
  \newblock {\em Eur. Phys. J.}, A6:329--344, 1999.

\bibitem{Eden:1994ji}
  T.~Eden et~al.
  \newblock {Electric form factor of the neutron from the
    $^{2}H(\vec{e},e’\vec{n})^{1}H$ reaction at $Q^{2} =$ 0.255 (GeV/c)$^2$}.
  \newblock {\em Phys. Rev.}, C50(4):R1749--R1753, 1994.

\bibitem{Glazier:2004ny}
  D.I. Glazier, M.~Seimetz, J.R.M. Annand, H.~Arenhovel, M.~Ases~Antelo, et~al.
  \newblock {Measurement of the electric form-factor of the neutron at Q$^2$ =
    0.3 (GeV$/c$)$^2$ to 0.8 (GeV/c)$^2$}.
  \newblock {\em Eur. Phys. J.}, A24:101--109, 2005.

\bibitem{Golak:2000nt}
  J.~Golak, G.~Ziemer, H.~Kamada, H.~Witala, and Walter Gloeckle.
  \newblock {Extraction of electromagnetic neutron form-factors through inclusive
    and exclusive polarized electron scattering on polarized $^3\!He$ target}.
  \newblock {\em Phys. Rev.}, C63:034006, 2001.

\bibitem{Herberg:1999ud}
  C.~Herberg, M.~Ostrick, H.G. Andresen, J.R.M. Annand, K.~Aulenbacher, et~al.
  \newblock {Determination of the neutron electric form-factor in the $D(e,e'
    n)p$ reaction and the influence of nuclear binding}.
  \newblock {\em Eur.Phys.J.}, A5:131--135, 1999.

\bibitem{Meyerhoff:1994ev}
  M.~Meyerhoff et~al.
  \newblock {First measurement of the electric form-factor of the neutron in the
    exclusive quasielastic scattering of polarized electrons from polarized
    $^3\!He$}.
  \newblock {\em Phys. Lett.}, B327:201--207, 1994.

\bibitem{Ostrick:1999xa}
  M.~Ostrick, C.~Herberg, H.G. Andresen, J.R.M. Annand, K.~Aulenbacher, et~al.
  \newblock {Measurement of the neutron electric form factor $G_{En}$ in the
    quasifree $^2\!H(\vec e,e'\vec n)p$ reaction}.
  \newblock {\em Phys. Rev. Lett.}, 83:276--279, 1999.

\bibitem{Passchier:1999ju}
  I.~Passchier et~al.
  \newblock {The Charge form-factor of the neutron from the reaction polarized
    $^2\!H (\vec e,e' n)p$}.
  \newblock {\em Nucl. Phys.}, A663:421--424, 2000.

\bibitem{Roberts:1994dr}
  Craig~D. Roberts and Anthony~G. Williams.
  \newblock {Dyson-Schwinger equations and their application to hadronic
    physics}.
  \newblock {\em Prog. Part. Nucl. Phys.}, 33:477--575, 1994.

\bibitem{Plaster:2005cx}
  B.~Plaster et~al.
  \newblock {Measurements of the neutron electric to magnetic form-factor ratio
    $G_{En} / G_{Mn}$ via the $^2\!H(\vec e, e'\vec n)^1\!H $ reaction to Q$^2$ =
    1.45 (GeV/c)$^2$}.
  \newblock {\em Phys. Rev.}, C73:025205, 2006.

\bibitem{Madey:2003av}
  R.~Madey et~al.
  \newblock {Measurements of $G_{En} / G_{Mn}$ from the $^2\!H (\vec e,e'\vec n)$
    reaction to Q$^2$ = 1.45 (GeV/c)$^2$}.
  \newblock {\em Phys. Rev. Lett.}, 91:122002, 2003.

\bibitem{Riordan:2010id}
  S.~Riordan et~al.
  \newblock {Measurements of the Electric Form Factor of the Neutron up to
    $Q^2=3.4$ GeV$^2$ using the Reaction $\vec{^3\! He}(\vec e,e'n)pp$}.
  \newblock {\em Phys. Rev. Lett.}, 105:262302, 2010.

\bibitem{PhysRevLett.35.632}
  R.~Diebold, D.~S. Ayres, S.~L. Kramer, A.~J. Pawlicki, and A.~B. Wicklund.
  \newblock {Measurement of the Proton-Neutron Elastic-Scattering Polarization
    from 2 to 6 GeV/c}.
  \newblock {\em Phys. Rev. Lett.}, 35:632--635, 1975.

\bibitem{Kramer:1977pf}
  S.~L. Kramer, D.~S. Ayres, Daniel~H. Cohen, R.~Diebold, A.~J. Pawlicki, and
  A.~B. Wicklund.
  \newblock {Polarization Parameter for Nucleon-Nucleon Elastic Scattering at
    11.8-GeV/c}.
  \newblock {\em Phys. Rev.}, D17:1709, 1978.

\bibitem{Spinka:1983rz}
  H.~Spinka et~al.
  \newblock {Beam polarization at the ZGS}.
  \newblock {\em Nucl. Instrum. Meth.}, 211:239--261, 1983.

\bibitem{Alekseev:1999ag}
  I.~G. Alekseev et~al.
  \newblock {Measurement of the carbon analyzing power for the momenta range 1.35
    GeV$/c$ to 2.02 GeV$/c$}.
  \newblock {\em Nucl. Instrum. Meth.}, A434:254--260, 1999.

\bibitem{Ladygin:409018}
  V.~P. Ladygin.
  \newblock {Analyzing power of $pp$ and $np$ elastic scattering at momenta
    between 2000 and 6000 MeV/c and polarimetry at LHE}.
  \newblock Technical Report E13-99-123, Joint Inst. Nucl. Res., Dubna, 1999.

\bibitem{PhysRevLett.30.1183}
  M.~A. Abolins, M.~T. Lin, R.~C. Ruchti, J.~G. Horowitz, R.~C. Kammerud, N.~W.
  Reay, et~al.
  \newblock {Measurement of the Polarization Parameter in $np$ Charge-Exchange
    Scattering from 2 to 12 GeV/c}.
  \newblock {\em Phys. Rev. Lett.}, 30:1183--1185, 1973.

\bibitem{Robrish:1970jw}
  P.~R. Robrish et~al.
  \newblock {Backward $n p$ scattering with a polarized target}.
  \newblock {\em Phys. Lett.}, 31B:617--620, 1970.

\bibitem{Kirillov:1996zf}
  A.~Kirillov et~al.
  \newblock {Relativistic polarized neutrons at the Laboratory of High-Energy
    Physics, JINR}.
  \newblock In {\em {Particles and nuclei. Proceedings, 14th International
      Conference, PANIC'96, Williamsburg, USA, May 22-28, 1996}}, pages 749--751,
  1996.

\bibitem{Sharov:2004pg}
  V.~I. Sharov et~al.
  \newblock {Measurement of the $ n p$ total cross section difference
    $\Delta\sigma_L(np)$ at 1.39-GeV, 1.69-GeV, 1.89-GeV and 1.99-GeV}.
  \newblock {\em Eur. Phys. J.}, C37:79--90, 2004.

\bibitem{Agapov:2004uu}
  N.~N. Agapov, V.~V. Fimushkin, V.~P. Vadeev, V.~P. Derenchuk, and A.~S. Belov.
  \newblock {IUCF polarized ion source CIPIOS for JINR accelerator nuclotron}.
  \newblock In {\em {Spin physics. Polarized electron sources and polarimeters.
      Proceedings, 16th International Symposium, SPIN 2004, Trieste, Italy, October
      10-16, 2004, and Workshop, PESP 2004, Mainz, Germany, October 7-9, 2004}},
  pages 774--775, 2004.

\bibitem{Fimushkin:2016uu}
  V~Fimushkin, A~D Kovalenko, L~V Kutuzova, Yu~V Prokofichev, B~Shutov, A~S
  Belov, V~N Zubets, and A~V Turbabin.
  \newblock {Development of polarized ion source for the JINR accelerator
    complex}.
  \newblock {\em {Journal of Physics: Conference Series}}, 679(1):012058, 2016.

\bibitem{abragam1961}
  A.~Abragam.
  \newblock {\em The Principles of Nuclear Magnetism}.
  \newblock Number~32. Oxford University Press, 1961.

\bibitem{Kuehn:1995hy}
  B.~Kuehn, C.~F. Perdrisat, and E.~A. Strokovsky.
  \newblock {Correlations between polarization observables in inclusive deuteron
    breakup}.
  \newblock {\em Phys. Atom. Nucl.}, 58:1795--1800, 1995.
  \newblock [Yad. Fiz.58,1898(1995)].

\bibitem{Rukoyatkin:2001nd}
  P.~Rukoyatkin.
  \newblock {Relativistic polarized beams for experiments on the polarized proton
    target at the Laboratory of High Energies}.
  \newblock {\em Czech. J. Phys.}, 51:A345--A350, 2001.

\bibitem{Bystricky:1981}
  J.~Bystricky and F.~Lehar.
  \newblock Nucleon-nucleon scattering data.
  \newblock {\em Fachinformation-szentrum Karlsuhe}, 11, 1981.

\bibitem{Bonin:1989tg}
  B.~Bonin et~al.
  \newblock {Measurement of the inclusive $pC$ Analyzing Power and Cross-section
    in the 1 GeV Region and Calibration of the New Polarimeter POMME}.
  \newblock {\em Nucl. Instrum. Meth. A}, 288:379, 1990.

\bibitem{Lehar:1996cr}
  F.~Lehar et~al.
  \newblock {Measurement of the total cross-section difference $\Delta
    \sigma—L$ in $n p$ transmission at 1.19-GeV, 2.49-GeV and 3.65-GeV}.
  \newblock {\em Z. Phys.}, C71:65--74, 1996.

\bibitem{Strela:2013}
  V.V. Glagolev et~al.
  \newblock {STRELA Experimental Setup for studying Charge-Exchange Processes}.
  \newblock {\em Nucl. Exp. Tech.}, 56:387--397, 2013.

\bibitem{Vlasov:2006}
  N.~V. Vlasov et~al.
  \newblock {A calorimeter for detecting hadrons with energies of 10-100 GeV}.
  \newblock {\em Instrum. Exp. Tech.}, 49(1):41--55, 2006.

\bibitem{abbon:2007}
  Ph. Abbon, E.~Albrecht, V.~Yu. Alexakhin, Yu. Alexandrov, G.D. Alexeev, M.G.
  Alekseev, A.~Amoroso, H.~Angerer, V.A. Anosov, B.~Bade{\l}ek, et~al.
  \newblock {The COMPASS experiment at CERN}.
  \newblock {\em Nucl. Instrum. Meth. A}, 577(3):455--518, 2007.

\bibitem{Sitnik:2014zwa}
  I.~M. Sitnik.
  \newblock {Development of the FUMILI minimization package}.
  \newblock {\em Comput. Phys. Commun.}, 185:599--603, 2014.

\bibitem{Kreisler-SLAC1966}
  M.N. Kreisler et~al.
  \newblock {Neutron-proton elastic scattering from 1 to 6.3 GeV}.
  \newblock Technical report, Stanford University, SLAC Report n. 66, 1966.

\bibitem{Gibbard:1971rt}
  B.~G. Gibbard, M.~J. Longo, Lawrence~W. Jones, J.~R. O'~Fallon, M.~N. Kreisler,
  and M.~L. Perl.
  \newblock {Neutron-proton elastic scattering from 5 to 30 GeV/c}.
  \newblock {\em Nucl. Phys.}, B30:77--115, 1971.

\bibitem{Jaros:1977it}
  J.~Jaros et~al.
  \newblock {Nucleus-Nucleus Total Cross-Sections for Light Nuclei at
    1.55-GeV/c/Nucleon and 2.89-GeV/c/Nucleon}.
  \newblock {\em Phys. Rev.}, C18:2273--2292, 1978.

\bibitem{Savin:2016arw}
  I.~Savin, A.~Efremov, D.~Peshekhonov, A.~Kovalenko, O.~Teryaev, O.~Shevchenko,
  A.~Nagajcev, A.~Guskov, V.~Kukhtin, and N.~Toplilin.
  \newblock {Spin physics experiments at NICA-SPD with polarized proton and
    deuteron beams}.
  \newblock {\em Eur. Phys. J.}, A52(8):215, 2016.

\bibitem{Sitnik:2016xxx}
  I.~M. Sitnik.
  \newblock {Development of the FUMILIM minimization package}.
  \newblock {\em Comput. Phys. Commun.}, 209:199, 2016.

\end{thebibliography}
